\cvsection{Professional Experience}

\begin{cventries}
  \cventry
    {Research Intern (Summer)}
    {\textsemibold{MIT–IBM Watson AI Lab}}
    {Cambridge, MA, USA}
    {2025}
    {
      \begin{cvitems}
        \item {Developed a knowledge-graph–augmented RAG framework for LLMs using multi-turn reinforcement learning (RL), achieving state-of-the-art accuracy with 47\% lower generation cost and 6\% higher transferability compared with prior methods.}
      \end{cvitems}
    }

  \cventry
    {Research Fellow}
    {Machine Learning Alignment and Theory Scholars}
    {Berkeley, CA, USA}
    {2025}
    {
      \begin{cvitems}
        \item {Proposed a novel, goal-agnostic evaluation framework for LLM agents using the information-theoretic measure (i.e empowerment : mutual information between actions and future states).}
      \end{cvitems}
    }

      \cventry
    {Graduate Research Assistant (PI: Prof. Jeff Gore)}
    {MIT}
    {Cambridge, MA, USA}
    {Feb 2021 -- Present}
    {
      \begin{cvitems}
        \item {Explored emergent phenomena (e.g., neural scaling behaviors, in-context learning) in LLMs, linking theories with empirical results.}
        \item {Developed a foundation model for human methylation data that predicts patient aging and chronic disease.}
        \item {Explored how interspecies interaction strength shapes the merging of two microbial communities using experiments and simulations.}
      \end{cvitems}
    }
    
  \cventry
    {Research Intern (Summer)}
    {Samsung Electronics Research}
    {Suwon, Korea}
    {2020}
    {
      \begin{cvitems}
        \item {Investigated post-quantum cryptography (lattice-based encryption methods) for use in DRAM products.}
      \end{cvitems}
    }

  \cventry
    {Research Intern (Summer)}
    {Harvard–MIT Health Sciences and Technology}
    {Boston, MA, USA}
    {2019}
    {
      \begin{cvitems}
        \item {Developed a neural connectome reconstruction algorithm that maps brain images into 3D space.}
      \end{cvitems}
    }
    
  \begin{comment}
  \cventry
    {Military Service}
    {Korea National Police Agency}
    {Korea}
    {2018}
    {
      \begin{cvitems}
        \item {Completed mandatory service; supported unit operations and logistics in a disciplined, team-based environment.}
      \end{cvitems}
    }
  \end{comment}


  \cventry
    {Undergraduate Research Assistant}
    {KAIST}
    {Daejeon, Korea}
    {Jul 2014 -- Aug 2020}
    {
      \begin{cvitems}
        \item {Biomedical Optics (PI: Prof. YongKeun Park): developed deep-learning algorithms for 3D time-lapse tracking of CAR-T cells; built classification models using 3D refractive-index maps for rapid pathogen identification.}
        \item {Chromatin/Protein Engineering (PI: Prof. Wonki Cho): implemented thermodynamic simulation code for multivalent antibody binding.}
        \item {Quantum \& Nanophotonics (PI: Prof. YongHoon Cho): investigated exciton–polariton coupling in GaN nanoporous DBR cavities.}
      \end{cvitems}
    }
    

\end{cventries}
