\cvsection{Publications}

{\small\textit{ * indicates equal contributions.}}

\vspace{-2mm}

\begin{cventries}
\cventry
{\textsemibold{\large AI related}}
{}
{}
{}
{
\begin{cvitemize2}
    \item \label{Blessing}Liang, Q., \textbf{Song, J.}, Liu, Y., Gore, J., Fiete, I.R., Miikkulainen, R., \& Qiu, X. ``The Blessing of Dimensionality in LLM Fine-tuning: A Variance-Curvature Perspective.'' \textit{arXiv preprint} (2026). \href{https://arxiv.org/abs/2602.00170}{\textcolor{link}{[PDF]}}
    \item \label{KG-R1}\textbf{Song, J.}, Wang, S., Shun, J., \& Zhu, Y. "Efficient and Transferable Agentic Knowledge Graph RAG via Reinforcement Learning." \textit{ICLR 2026, under review}. \href{https://jinyeop3110.github.io/assets/pdf/KG_R1_2026.pdf}{\textcolor{link}{[PDF]}}
    \newline \textit{$\hookrightarrow$ RL-tuned KG-RAG agent cutting generation cost 47\% with 6\% higher cross-domain transferability.}
    \item \label{EELMA}\textbf{Song, J.}, Gore, J. \& Kleiman, M. ``Estimating Empowerment of Language Model Agent'' \textit{arXiv preprint} (2025). \href{https://arxiv.org/pdf/2509.22504}{\textcolor{link}{[PDF]}}
    \newline \textit{$\hookrightarrow$ Goal-agnostic LLM-agent evaluation framework grounded in information-theoretic empowerment.}
    \item \label{Bayesian}Akke, M., Yang, S., Ru{\v{z}}a, J., \textbf{Song, J.}, Pan, E., \& G{\'o}mez-Bombarelli, R.
    \emph{When Do LLMs Improve Bayesian Optimization? A Systematic Comparison Across Molecular and Protein Design}.
    \textit{NeurIPS 2025, AI4Science Workshops}. \href{https://openreview.net/forum?id=x3Y2TwVXwE#discussion}{\textcolor{link}{[PDF]}}
    \item \label{SPOT}Son, G., Hong, J., Fan, H., Nam, H., Ko, H., Lim, S., \textbf{Song, J.}, Choi, J., Paulo, G., Yu, Y., \& Biderman, S. "When AI Co-Scientists Fail: SPOT - Benchmark for Automated Verification of Scientific Research." \textit{arXiv preprint} (2025) \href{https://arxiv.org/pdf/2505.11855}{\textcolor{link}{[PDF]}},
    \item \label{ICL}\textbf{Song, J.*}, Han, S.*, Argawal, P., \& Gore, J. ``Emergence and Effectiveness of Task Vectors in In-Context Learning : An Encoder Decoder Perspective'' \textit{ICML 2025, \textbf{Spotlight}} \href{https://arxiv.org/pdf/2412.12276}{\textcolor{link}{[Link]}},
    \newline \textit{$\hookrightarrow$ First encoder--decoder analysis showing transformers form compact task vectors that causally drive in-context predictions.}
    \item \label{ID-Chem}Yang, S., Nam, J., Perez, T., \textbf{Song, J.}, Du, X., \& Gomez-Bombarelli, R. ``Probing the Embedding Space of Protein Foundation Models through Intrinsic Dimension Analysis'' \label{Protein}\textit{Neurips 2025, AIDrugX Workshop}\href{https://openreview.net/forum?id=r9OUQpwhVo}{\textcolor{link}{[Link]}},
    \item \label{MethylGPT}Ying, A.*, \textbf{Song, J.*}, Cui. H.* ... et al.  ``MethylGPT - Foundational GPT-like model for human methylation data'' \textit{2024}.  \href{https://www.biorxiv.org/content/10.1101/2024.10.30.621013v1}{\textit{submitted for Nature Methods} \textcolor{link}{[Link]}}
    \newline \textit{$\hookrightarrow$ Co-led GPT-style foundation model on 226k methylation profiles; state-of-the-art disease/age prediction.}
    \item \label{Reconcile_Kaplan_Chinchilla}Pearce, T., \& \textbf{Song, J} ``Reconciling Kaplan and Chinchilla Scaling Laws'' \textit{TMLR}, 2024.  \href{https://arxiv.org/abs/2406.12907}{\textcolor{link}{[Link]}}
    \item \label{Resource_model}\textbf{Song, J.*}, Liu, Z.*, Tegmark, M., \& Gore, J. ``Resource model for neural scaling law,''  \textit{2024 ICRL, BGPT Workshop}, 2024.  \href{https://arxiv.org/abs/2402.05164}{\textcolor{link}{[Link]}}
\end{cvitemize2}
}


\vspace{1mm}
\cventry
{\textsemibold{\large Biophysics related}} % Empty position
{}
{}
{}
{
\begin{cvitemize2}
    \item \textbf{Song, J.}, Hu, J. \& Gore, J. ``Interspecies Interaction Shapes Community-level Selection in Microbial Coalescence,'' \textit{In Preparation}, 2025. \href{https://jinyeop3110.github.io/assets/pdf/Coalescence_main_2026.pdf}{\textcolor{link}{[PDF]}} \href{https://jinyeop3110.github.io/assets/pdf/Coalescence_supplementary_2026.pdf}{\textcolor{link}{[Supp]}}
    \item \textbf{Song, J.*}, Jeong, B.S.*, ..., \& Oh, B.H. ``Noncovalent antibody catenation on a target surface greatly increases the antigen-binding avidity,'' \textit{Elife}, 9: e81646, 2023.  \href{https://elifesciences.org/articles/81646}{\textcolor{link}{[Link]}}
    \item Lee, M.*, Lee, Y. H.*, \textbf{Song, J.*}, ..., \& Park, Y. ``Deep-learning-based three-dimensional label-free tracking and analysis of immunological synapses of CAR-T cells,'' \textit{Elife}, 9, 2020.  \href{https://elifesciences.org/articles/49023}{\textcolor{link}{[Link]}}
    \item Kim, G., Ahn, D., Kang, M., Jo, Y., Ryu, D., Kim, H., \textbf{Song, J.}, ..., \& Kim, K. ``Rapid species identification of pathogenic bacteria from a minute quantity exploiting three-dimensional quantitative phase imaging and artificial neural network,'' \textit{Light, Science \& Applications}.  \href{https://www.nature.com/articles/s41377-022-00881-x}{\textcolor{link}{[Link]}}
\end{cvitemize2}
}

\end{cventries}
