\cvsection{Publications}

\begin{cventries}

* indicate equal contributions. 

\cventry
{}
{}
{} 
{} 
{   	
\begin{cvitemize2}
    \item \textbf{Song, J.*}, Han, S.*, Argawal, P., \& Gore, J. ``Context to Concept : Concept Encoding in In-context learning'' \label{ICL} \textit{Submitted for ICLR 2025}, 2024.  \href{https://jinyeop3110.github.io/projects/1_project/}{\textcolor{link}{[Link]}}
    \newline
    \item Yang, S., Nam, J., Perez, T., \textbf{Song, J.}, Du, X., \& Gomez-Bombarelli, R. ``Probing the Embedding Space of Protein Foundation Models through Intrinsic Dimension Analysis'' \label{Protein}\textit{Neurips 2025 AIDrugX workshop}, 2024.  
    \newline
    \item Ying, A.*, \textbf{Song, J.*}, Cui. H.* ... et al. \label{MethylGPT} ``MethylGPT - Foundational GPT-like model for human methylation data'' \textit{2024}.  \href{https://www.biorxiv.org/content/10.1101/2024.10.30.621013v1}{\texit{submitted for Nature Methods} \textcolor{link}{[Link]}}
    \newline
    \item Pearce, T., \& \textbf{Song, J} ``Reconciling Kaplan and Chinchilla Scaling Laws'' \textit{In review process in TMLR}, 2024. \label{Reconcile_Kaplan_Chinchilla}\href{https://arxiv.org/abs/2406.12907}{\textcolor{link}{[Link]}}
    \item \textbf{Song, J.*}, Liu, Z.*, Tegmark, M., \& Gore, J. ``Resource model for neural scaling law,'' \label{Resource_model} \textit{2024 ICRL Workshop - Bridging the Gap Between Practice and Theory in Deep Learning}, 2024.  \href{https://arxiv.org/abs/2402.05164}{\textcolor{link}{[Link]}}
    \item \textbf{Song, J.*}, Jeong, B.S.*, ..., \& Oh, B.H. ``Noncovalent antibody catenation on a target surface greatly increases the antigen-binding avidity,'' \textit{Elife}, 9: e81646, 2023.  \href{https://elifesciences.org/articles/81646}{\textcolor{link}{[Link]}}
    \vspace{1mm}
    \item Lee, M.*, Lee, Y. H.*, \textbf{Song, J.*}, ..., \& Park, Y. ``Deep-learning-based three-dimensional label-free tracking and analysis of immunological synapses of CAR-T cells,'' \textit{Elife}, 9, 2020.  \href{https://elifesciences.org/articles/49023}{\textcolor{link}{[Link]}}
    \vspace{1mm}
    \item Kim, G., Ahn, D., Kang, M., Jo, Y., Ryu, D., Kim, H., \textbf{Song, J.}, ..., \& Kim, K. ``Rapid species identification of pathogenic bacteria from a minute quantity exploiting three-dimensional quantitative phase imaging and artificial neural network,'' \textit{Light, Science \& Applications}.  \href{https://www.nature.com/articles/s41377-022-00881-x}{\textcolor{link}{[Link]}}
\end{cvitemize2}
}


\end{cventries}