\cvsection{Research Projects}
\begin{cventries}

  \cventry
    {PhD Candidate (PI: Prof. Jeff Gore)} % Position
    {Laboratory of Complex Intelligence, MIT} % Project
    {Boston, MA} % Location
    {June 2023 - Present} % Date
    { 
      \begin{cvitems}
        \item{(1) Investigating the latent contextual knowledge structures of LLMs.}
        \item{(2) Exploring emergent phenomena, such as  neural scaling laws.}
      \end{cvitems}
    }
        \vspace{1mm}
        
  \cventry
    {PhD Candidate (PI: Prof. Jeff Gore)} % Position
    {Laboratory of Complex Ecosystems, MIT} % Project
    {Boston, MA} % Location
    {Feb 2021 - Present} % Date
    { 
      \begin{cvitems}
        \item{Employing complex physics approach to understand (1) generic pattern of microbial coalescence and community cohesiveness.}
        \item{(2) Emergent pattern of evolution of multispecies community.}
      \end{cvitems}
    }
        \vspace{1mm}

  \cventry
    {Research Assistant (PI: Prof. Wonki Cho)} % Position
    {Laboratory of Chromatin Imaging, KAIST} % Project
    {Daejeon, Korea} % Location
    {Feb 2020 - Present} % Date
    { 
      \begin{cvitems}
        \item{Developed thermodynamic simulation code for multivariate Antibody binding.}
      \end{cvitems}
    }
        \vspace{1mm}

  \cventry
    {Undergraduate Researcher (PI: Prof. YongKeun Park)} % Position
    {Laboratory of Biomedical Optics, KAIST} % Project
    {Daejeon, Korea} % Location
    {Feb 2018 - Aug 2020} % Date
    { 
      \begin{cvitems}
        \item{Developed deep-learning based computational algorithm for 3D time-lapse tracking of T-cell(CAR-T).}
        \item{Imaged and analyzed 3D refractive index map of sepsis bacterial pathogens for classification model.}
      \end{cvitems}
    }
\vspace{1mm}
  \cventry
    {Research Intern (PI: Prof. Brett Bouma)} % Position
    {Biomedical OCT Research Center, Massachusetts General Hospital} % Project
    {Boston, MA, USA} % Location
    {Jun 2019 - Aug 2019} % Date
    { 
      \begin{cvitems}
        \item{Developed computational analysis pipeline for mapping brain image to mural connectome.}
      \end{cvitems}
    }
\vspace{4mm}

  \cventry
    {Undergraduate Researcher (PI: Prof. YongHoon Cho)} % Position
    {Laboratory of Quantum and Nanophotonics, KAIST} % Project
    {Daejeon, Korea} % Location
    {Jul 2014 - Feb 2015} % Date
    { 
      \begin{cvitems}
        \item{Investigated exciton-polariton coupling effect of GaN nanoporous DBR cavity using FDTD simulation and optical experiments.}
      \end{cvitems}
    }
\end{cventries}